Variable Density Tesseroids: Gravity fields calculation in spherical coordinates using variable densities in depth

### 2017-08-18 manuscript/manuscript.tex
Minor changes in manuscript

We have recorded the computation times for the gravity potential, the gradient component $g_z$ and the Marussi tensor component $g_{zz}$ generated by a single tesseroid model with homogeneous and variable density at different heights (see Figure \ref{fig:speed-comparison}).
Firstly, we can see that both codes take more time to compute the gravity field for lower heights due to the increased divisions of the tesseroid in such cases.
Secondly, we can see that the homogeneous density code is up to twice faster than the new variable density algorithm, however the later is fast enough to perform the calculations of a real model in a few minutes. \todo{real, esta bien la expresion?}

@@

We computed the three gravity fields for different values of $D$, ranging from 0.5 to 10 with a step of 0.5, on every point of these four grids.
Then, we calculated the maximum difference between these results and the value of the analytical solution at the same height.

@@

Finally, we set the acceptable value of $D$ at which the error of the numerical approximation is lower than 0.1\%.

@@

\begin{equation}
    \rho(r') = 
    -\frac{3300 - 2670}{35000} r' + 
    \left( \frac{3300 - 2670}{35000} R + 2670 \right)
    \label{eq:density-linear}
\end{equation}

>>>>

We have recorded the computation times for the gravity potential, the gradient component $g_z$ and the Marussi tensor component $g_{zz}$ generated by a single tesseroid model with homogeneous and variable density at different heights (see Figure \ref{fig:speed-comparison}).
Firstly, we can see that both codes take more time to compute the gravity field for lower heights due to the increased divisions of the tesseroid in such cases.
Secondly, we can see that the homogeneous density code is up to twice faster than the new variable density algorithm for lower heights, however the computation times gets more similar values at greater heights. In conclusion, the new variable dnesity code is fast enough to perform the calculations of a real model in a few minutes. \todo{real, esta bien la expresion?}

@@

We computed the three gravity fields for different values of $D$, ranging from 0.5 to 10 with a step of 0.5, on every point of these four grids.
Then we calculated the maximum difference between these results and the value of the analytical solution at the same height.

@@

Finally, we set the acceptable value of $D$ if the corresponding error of the numerical approximation is lower than 0.1\%.

@@

\begin{equation}
    \rho(r') = ar' + c,
    %~ -\frac{3300 - 2670}{35000} r' + 
    %~ \left( \frac{3300 - 2670}{35000} R + 2670 \right)
    \label{eq:density-linear}
\end{equation}
\noindent with 
\begin{equation}
    a = -\frac{3300\text{kg/m$^3$} - 2670\text{kg/m$^3$}}{35000\text{m}},
\end{equation}
\begin{equation}
    c = \frac{3300\text{kg/m$^3$} - 
        2670\text{kg/m$^3$}}{35000\text{m}} R + 
        2670\text{kg/m$^3$},
\end{equation}
